---
format: 
  pdf:
    documentclass: article
    engine: knitr
    date-format: "DD.MM.YYYY"
    toc: false
    documentclass-options: titlepage
    header-includes: |
      \usepackage[margin=1in]{geometry} 
      \usepackage{titling}
      \setlength{\droptitle}{-2em} 
      \usepackage{array}
      \renewcommand{\arraystretch}{1.5}
      \usepackage{graphicx}
bibliography: references.bib
editor: visual
---

\begin{titlepage}
  \centering
  \vspace*{2cm}
  
  \includegraphics[width=0.6\textwidth]{HU_logo.png} 
  \vspace{0.5cm}
  
  {\huge Assignment 1 - Empirical Assignment \par}
  \vspace{1cm}
  
  {\Huge\bfseries Research Log \par}
  \vspace{2cm}
  
  {\Large Research on Corporate Transparency (SoSe 2025) \par}
  \vspace{0.5cm}
  
  {\Large 708016 \par}
  \vspace{0.5cm}
  
  {\Large Prof. Dr. Joachim Gassen \par}
  \vspace{0.5cm}
  
  {\Large Valentine Pasqualina Lassagne, 499198 \par}
  \vfill
  
  {\large \today \par}
\end{titlepage}
\tableofcontents
\newpage

# Step 1: Identifying Local Firms

*08.05.2025*

To complete Task 1, I began by identifying firms I had noticed while walking around in my neighbourhood. I currently live in Wedding with postal code **13359**. The first one was a restaurant called *Lalibela*. After checking its *Impressum*, I found that its registered address did not fall under the postal code 13359. The second firm was *Wohlfarth Schokolade*, which was indeed registered within postal code 13359.

Following this, I asked my roommate if she knew of any businesses of any type, including firms, shops and services. She recommended a restaurant called *El Pepe*, mentioning that it was worth a visit. I, therefore, checked its *Impressum* and it is registered under the postal code 13359.

As a next step, I searched for businesses within my postal code using Google Maps. My main focus was on food, creativity and sports, as I am particularly interested in exploring these types of places in my neighbourhood. The results of my search are summarized in the two tables below.

**Table 1: Firms registered under the postal code 13359**

| Firm Name on Google Maps | Official Firm Name | Address |
|------------------------|------------------------|------------------------|
| [Afro United Salon](https://www.google.com/maps/place/Afro+United+Salon/@52.5611636,13.3861772,17z/data=!3m1!4b1!4m6!3m5!1s0x47a8538bbb66e083:0x5ab9a73e92f768d!8m2!3d52.5611636!4d13.3887575!16s%2Fg%2F11qyp3gy83?entry=ttu&g_ep=EgoyMDI1MDUxNS4wIKXMDSoASAFQAw%3D%3D) | [Afro United Salon](https://afrounitedsalon.de/impressum/) | Wollankstrasse 72, 13359 Berlin |
| [Event Rental Hempel GmbH](https://www.google.com/maps/place/Event+Rental+Hempel+GmbH/@52.5617804,13.3776516,16z/data=!3m1!4b1!4m6!3m5!1s0x47a85230ae49f0c3:0xa8f283e252187175!8m2!3d52.5617804!4d13.3802319!16s%2Fg%2F11bcdhr95v?entry=ttu&g_ep=EgoyMDI1MDUxNS4wIKXMDSoASAFQAw%3D%3D) | [EventRental HEMPEL GmbH](https://eventrental.de/impressum/) | Holzstrasse 6a, 13359 Berlin |
| [Wohlfarth Schokolade](https://www.google.com/maps/place/Wohlfarth+Schokolade/@52.560049,13.3792608,17z/data=!3m2!4b1!5s0x47a8523a42fd230d:0xab1f0e365ee11797!4m6!3m5!1s0x47a851fdd4b42517:0x9e5ca2a56af39d91!8m2!3d52.560049!4d13.3818411!16s%2Fg%2F1hc1ht7yn?entry=ttu&g_ep=EgoyMDI1MDUxNS4wIKXMDSoASAFQAw%3D%3D) | [Wohlfarth Schokolade](https://www.wohlfarthschokolade.de/de/info/impressum.html) | Soldiner Strasse 39, 13359 Berlin |
| [El Pepe](https://www.google.com/maps/place/El+Pepe/@52.5566747,13.3826009,17z/data=!3m1!4b1!4m6!3m5!1s0x47a8523b513ab1bd:0x8cb64b3d5fd30555!8m2!3d52.5566747!4d13.3851812!16s%2Fg%2F11bymw6dkh?entry=ttu&g_ep=EgoyMDI1MDUxNS4wIKXMDSoASAFQAw%3D%3D) | [El Pepe Tapas Bar](https://elpepetapasbar.de/impressum/) | Prinzenallee 25, 13359 Berlin |
| [BAS CS Gallery](https://www.google.com/maps/place/BAS+CS+Gallery/@52.5573366,13.3878549,17z/data=!3m2!4b1!5s0x47a8523d1b8b2401:0x1d82340dd66ab117!4m6!3m5!1s0x47a8536ee842def1:0xf51d6635d3ba110d!8m2!3d52.5573366!4d13.3904352!16s%2Fg%2F11ll6j56n7?entry=ttu&g_ep=EgoyMDI1MDUxNS4wIKXMDSoASAFQAw%3D%3D) | [Bas CS Gallery](https://bas-cs-gallery.de/impressum/) | Soldiner Strasse 103, 13359 Berlin |

**Table 2: Firms not registered under the postal code 13359**

| Firm Name on Google Maps | Official Firm Name | Google Maps Address | Registered Address |
|------------------|------------------|------------------|------------------|
| [Effect Defense Tækwondo + Selbstverteidigung in Berlin Mitte](https://www.google.com/maps/place/Effect+Defense+Taekwondo+%2B+Selbstverteidigung+in+Berlin+Mitte/@52.55656,13.38076,16z/data=!3m1!4b1!4m6!3m5!1s0x47a852253286b2c9:0xb91e117315f45937!8m2!3d52.55656!4d13.38076!16s%2Fg%2F11hbr1hj3p?entry=ttu&g_ep=EgoyMDI1MDUxNS4wIKXMDSoASAFQAw%3D%3D) | [Sultans e.V.](http://effect-defense.de/impressum/) | Osloer Strasse 24, 13359 Berlin | Cauerstrasse 15, 10587 Berlin |
| [POCO Berlin - Wedding](https://www.google.com/maps/place/POCO+Berlin+-+Wedding/@52.5577185,13.3732627,17z/data=!3m1!5s0x47a8523049d6cf11:0x971e7b46e5bd86c8!4m15!1m8!3m7!1s0x47a8523a11130799:0x1c212049953ffa60!2s13359+Berlin,+Allemagne!3b1!8m2!3d52.5591664!4d13.3830433!16s%2Fg%2F1tdx7r9f!3m5!1s0x47a852304393191d:0x45bfdeafdc8292bf!8m2!3d52.55858!4d13.37651!16s%2Fg%2F1vp72tg6?entry=ttu&g_ep=EgoyMDI1MDUxNS4wIKXMDSoASAFQAw%3D%3D) | [POCO Einrichtungsmärkte GmbH](https://www.poco.de/c/impressum) | Drontheimer Strasse 30a, 13359 Berlin | Industriestrasse 39, 59192 Bergkamen |
| [Lalibela Restaurant - Taste of Ethiopia, Wedding](https://www.google.com/maps/place/13359+Berlin,+Allemagne/@52.5607201,13.3405174,13z/data=!3m1!4b1!4m6!3m5!1s0x47a8523a11130799:0x1c212049953ffa60!8m2!3d52.5591664!4d13.3830433!16s%2Fg%2F1tdx7r9f?entry=ttu&g_ep=EgoyMDI1MDUxNS4wIKXMDSoASAFQAw%3D%3D) | [Lalibela GmbH](http://lalibelawedding.de/impressum/) | Soldiner Strasse 41, 13359 Berlin | Lauterstraße 11a, 12159 Berlin |

# Step 2: Local Firms in Corporate Register

*12.05.2025*

For Task 2, I searched for the firms selected in Step 1 on the website <https://www.unternehmensregister.de/ureg/>. My results are summarized in the tables below.

**Table 3: Register Information**

| Official Firm Name      | Registered | Registered Company Name | Register Number |
|------------------|------------------|------------------|------------------|
| Afro United Salon       | No         | \-                      | \-              |
| EventRental HEMPEL GmbH | Yes        | EventRental Hempel GmbH | HRB 26423       |
| Wohlfarth Schokolade    | No         | \-                      | \-              |
| El Pepe Tapas Bar       | No         | \-                      | \-              |
| Bas CS Gallery          | No         | \-                      | \-              |

**Table 4: Financial Statements**

| Official Firm Name | Financial Statements | Type | Latest Fiscal Start Date | Latest Fiscal End Date | Date of Filing |
|------------|------------|------------|------------|------------|------------|
| Afro United Salon | \- | \- | \- | \- | \- |
| EventRental HEMPEL GmbH | Available | Single Legal Entity | 01.01.2023 | 31.12.2023 | 04.03.2025 |
| Wohlfarth Schokolade | \- | \- | \- | \- | \- |
| El Pepe Tapas Bar | \- | \- | \- | \- | \- |
| Bas CS Gallery | \- | \- | \- | \- | \- |

Among those firms, only *EventRental HEMPEL GmbH* had data available. Financial statements are accessible for the years 2007 to 2023. For the other businesses, one possible reason for the absence of registration could be that they are newly established. However, according to the websites of *Afro United Salon* and *Wohlfarth Schokolade*, these businesses have been operating since 2021 and 2020, respectively. No founding dates were provided for the remaining two firms.

Regarding *Bas CS Gallery*, it is part of *Kolony Wedding e.V.*, a non-profit organization that hosts exhibitions and other cultural activities. This explains why it is not listed.

Finally, another reason for the lack of registration could be that these businesses are sole proprietors. Unlike *EventRental HEMPEL GmbH*, the *Impressum* sections of *Afro United Salon, Wohlfarth Schokolade* and *El Pepe Tapas Bar* include the full name of an individual, which confirms that these three are likely operated as sole proprietorships.

# Step 3: Orbis Data

*20.05.2025*

I cloned the repository to my local desktop using the following command in the terminal:

`bash git clone https://github.com/joachim-gassen/rct25.git`

Next, I downloaded the Orbis data from Moodle in my personal file and copied it into the `data/generated` folder of the `rct25` project using the command below:

`bash cp ~/Desktop/Research\ on\ Corporate\ Transparency/Assignment\ 1/orbis_panel_berlin.rds ~/Desktop/rct25/data/generated`

I imported the dataset into R and started by inspecting its structure and contents using the `str()` and `summary()` functions. To check whether a specific firm appeared in the dataset, I created a function `check_firm_name(data, firm_name)` that compares the given name to the `name_native` column. If a match is found, the function prints "yes" along with the years in which financial statements are available. When applied to *EventRental Hempel GmbH*, the function returned entries for the years 2012 through 2021.

```{r}
#| include: false
# hidden setup code
library(dplyr)

orbis_data <- readRDS("data/generated/orbis_panel_berlin.rds")

str(orbis_data)
summary(orbis_data) 

check_firm_name <- function(data, firm_name) {
  match_rows <- data[data$name_native == firm_name, ]
  
  if (nrow(match_rows) > 0) {
    cat("yes\n")
    cat("year(s):", paste(match_rows$year, collapse = ", "), "\n")
  } else {
    cat("no\n")
  }
}

check_firm_name(orbis_data, "EventRental Hempel GmbH")

```

# Step 4: Largest Firm in Orbis with Postal Code 13359

*20.05.2025*

For this task, I filtered the data to include only firms with postal code **13359** and a reporting year of **2021**. I then created a new dataset by sorting the firms in descending order based on total assets (`toas`, as defined in the Orbis data guide). The top entry, *USE*, [*Union Sozialer Einrichtungen gemeinnützige GmbH*](https://www.unternehmensregister.de/ureg/result.html;jsessionid=4237FE88389F66484F4BC91F1E317F89.web04-1?submitaction=showDocument&id=32035317), had its 2021 financial report available.

*23.05.2025*

From the Orbis database, I retrieved the firm's total assets (`toas`), the book value of equity (`shfd`) and the net sales (`turn`). According to the Orbis documentation, the book value of equity is composed of capital (`capi`) and other shareholders' funds (`osfd`). I then downloaded the 2021 financial statement of *USE*. From the income statement, I obtained the net sales. From the balance sheet, I identified the total assets and the book value of equity, which consists of capital, retained earnings and special items with an equity portion and is calculated as:

```{=latex}
\begin{align*}
\textbf{BVE} &= \text{Capital} + \text{Retained Earnings} + \text{Special items with an equity portion} \\
          &= 26{,}000 + 9{,}605{,}603.11 + 3{,}816{,}081.35 \\
          &= 13{,}447{,}684.46
\end{align*}
```

**Table 5: Financial Comparison for USE (2021)**

| Metric               | Orbis      | Unternehmensregister |
|----------------------|------------|----------------------|
| Total Assets         | 20'334'294 | 20'334'294           |
| Book Value of Equity | 13'447'684 | 13'447'684           |
| Net Sales            | 33'756'421 | 33'756'421           |

The table above presents a summary of my findings. It shows that there is no difference between Orbis and Unternehmensregister data, as they align perfectly for the 2021 financial statement. After rounding values to the nearest whole number, the figures are identical. The matching data shows that the firm follows the rules and reports as required. However, it does not automatically mean the firm is fully transparent, just that it meets the basic legal obligations.

```{r}
#| include: false
# hidden setup code
data_postcode_13359_year_2021 <- orbis_data %>%
  filter(postcode == "13359", year == 2021)

str(data_postcode_13359_year_2021)

data_sorted_by_toas <- data_postcode_13359_year_2021 %>%
  arrange(desc(toas))

USE <- as.data.frame(t(data_sorted_by_toas[1, ]))

USE_TA <- USE["toas",]
USE_BVE <- USE["shfd",]
USE_NS <- USE["turn",]

```

# Step 5: Comparison of Firms with Postal Code 13359 to the Berlin Firm Population

*23.05.2025*

Following the approach of @mishra2019application, I conducted two two-sample, two-tailed t-tests to compare the mean total assets and mean equity ratio of two distinct groups of firms in 2021: those located in postal code 13359 and those in the rest of Berlin. The objective was to assess whether the observed differences between these two populations are statistically significant.

*28.05.2025*

Given the scope of the two t-tests, I focused only on data from the year 2021 rather than using the full panel. I added a new column to the dataset to calculate equity ratios, then created a dummy variable indicating whether a firm's postcode is **13359** (1) or not (0). Using this, I ran two two-sample t-tests to compare the mean total assets and, separately, the mean equity ratio between the two groups. I used the `tidy()` function to clean up both test results, with columns renamed for clarity. I then combined the two result tables together using `bind_rows()` and added a new leading column to indicate the variable being tested. The final table was formatted using LaTeX for better presentation.

While creating the final table, I encountered an issue that I have not been able to solve. I wanted my p-values to print "\< 0.001" when that was the case. However, with LaTeX, I did not manage to display this properly and instead got "¡ 0.001". I tried to use the same format as the other p-value, which is `as.character(round(p.value, 4))`, but then for a very small p-value, the value gets rounded to zero. I did not want that in my table since the true value would be hidden. That is why I chose to use the scientific notation for the first p-value. Therefore, we can still see the actual p-value.

*29.05.2025*

Based on the final table (see additional PDF), we can interpret the results. The table reports the mean values for the two variables being compared, namely *Total Assets* and *Equity Ratios*, along with their corresponding *t*-statistics, degrees of freedom, p-values and 95% confidence intervals, corresponding to a significance level of 0.05.

The mean total assets for firms in postcode 13359 is approximately €1.8 million, while for firms in all other postcodes is about €24.6 million. The *t*-statistic is roughly 6.16, which is considered quite large, indicating that the observed difference between the two groups is several standard errors away from zero. The degrees of freedom for this test is 25'734, reflecting the effective sample size after accounting for variance differences. The p-value is less than 0.001, indicating that the difference in means between the two groups is statistically significant and not equals to zero. Additionally, the 95% confidence interval (approximately €15.5 million to €30 million) does not include zero, further supporting the conclusion that the mean total assets differ significantly between firms in postcode 13359 and those elsewhere.

These results suggest that, on average, firms in my postal code are significantly smaller or potentially represent a less developed business environment compared to those in other areas. However, as noted in step 2, some firms are not registered, such as sole proprietors or informal businesses and therefore are not included in the dataset. This means the analysis may not capture the full economic activity in the postcode and this limitation applies to both groups being compared.

The mean equity ratio for firms in postcode 13359 is approximately -0.05, whereas for firms in all other postcodes it is around -46.87, an unusually large negative value. To understand this, I examined the summary statistics for shareholders’ funds (`shfd`), total assets (`toas`) and equity ratio using the `summary()` function. I focused primarily on the minimum and maximum values to gain insight into the reasons behind this extreme mean. The following table presents these summary values.

**Table 6: Selected Descriptive Statistics for Equity Ratio, Total Assets and Shareholders' Funds**

| Variable                   | Minimum      | Mean       | Maximum        |
|----------------------------|--------------|------------|----------------|
| Equity Ratios (shfd/toas)  | -1'001'000   | -46.33     | 1.00           |
| Total Assets (toas)        | 1.00         | 24'510'000 | 71'840'000'000 |
| Shareholders' Funds (shfd) | -657'000'000 | 8'704'000  | 22'040'000'000 |

The data shows that there are no negative values for total assets, but negative equity values do exist. This could indicate that some firms are in financial distress or have high levels of debt, meaning they owe more than they own. To gain further insight, I investigated how many firms had negative equity values within the two groups: those in postcode 13359 and those in other postcodes.

**Table 7: Summary of Firms with Negative Shareholders' Funds by Postal Code Group**

| Location Group (13359 or not) | Total Firms (count) | Firms with Negative Shareholders' Funds (shfd) |
|----|----|----|
| 1 | 56 | 11 |
| 0 | 27'680 | 4'502 |
| NA | 273 | 68 |

From both tables, we can understand why the mean equity ratio for firms outside postal code 13359 is so low. There are many firms with negative shareholders’ funds (`shfd`) in that group. In contrast, the mean equity ratio for firms in postal code 13359 is closer to zero, suggesting that on average, these firms have nearly neutral equity ratios. In other words, those firms' assets and liabilites are nearly balanced. Additionally, some firms were not assigned to either group (dummy 0 or 1) due to missing postcode data. These cases were excluded from the t-test analysis.

The *t*-statistic is approximately -1.27, which is relatively small in absolute value. With a large sample size, the degrees of freedom for this test is 27,682. The p-value is 0.20, indicating that the difference in mean equity ratios between the two groups is **not** statistically significant and can not be distinguished from zero at the 0.05 significance level. Furthermore, the 95% confidence interval, ranging from about -118.95 to 25.28, includes zero, reinforcing the conclusion that there is no significant difference in mean equity ratio between firms in postcode 13359 and those in other areas.

# Conclusion

Throughout this research log, I documented my process and findings in a structured manner. In Steps 1 and 2, I identified several firms from my postal code and verified their presence on <https://www.unternehmensregister.de/ureg/>. Only one of them had publicly available register and financial data. In Step 3, I downloaded the Orbis dataset and confirmed that the same firm was also included there. In Step 4, I identified the largest firm in my postal code based on total assets in Orbis and compared its financial data with the official filings on <https://www.unternehmensregister.de/ureg/>. The values matched. Finally, in Step 5, I performed two two-sample t-tests to compare mean total assets and equity ratios between firms located in postal code 13359 and those in the rest of Berlin. The results showed that firms in my postal code are significantly smaller in terms of total assets (p-value \< 0.001), while the difference in equity ratios was not statistically significant (p-value \> 0.05).

\newpage

# References
